Done

### 2025-07-15 done.qmd
update

@@

May - June: Sprint on AI in grantmaking

@@

2024-06-21: Research Matters magazine (with Shaun Leamon): [Experiments in research funding to reduce research](https://the-sra.org.uk/common/Uploaded%20files/Research%20Matters%20Magazine/sra-research-matters-june-2024-edition.pdf) bureaucracy

>>>>

2025-07-01 Science runs a story on our work on Distributed Peer Review: [Should grant applicants judge competitors’ proposals? Unorthodox approach gets two real-world tests](https://www.science.org/content/article/should-grant-applicants-judge-competitors-proposals-unorthodox-approach-gets-two-real) doi: 10.1126/science.zap69fh

2025-07-01 Quoted in Nature for this story on Distributed Peer Review: [How to speed up peer review: make applicants mark one another](https://www.nature.com/articles/d41586-025-02090-z). Nature 643, 313-314 (2025) doi: https://doi.org/10.1038/d41586-025-02090-z

June 29th: Helped organise and run ECR Metascientst Happy Hour, a networking event before Metascience 2025 hosted by the UKRN. Report: [How to make a career in Metascience: Advice from Experts](https://www.ukrn.org/2025/07/04/ecr-metascientist-happy-hour/)

@@

May : external advisor and auditor for UKRI's first trial of Distributed Peer Review (read about this in their report [A Year in Metascience](https://www.gov.uk/government/publications/a-year-in-metascience-2025), published 2025-06-30)

May - June: [AFIRE Sprint on AI in grantmaking](https://researchonresearch.org/afire-ai-in-funding-sprint/)

2025-03-04: Chaired the [UKRN](https://www.ukrn.org/) Institutional Leads retreat in Cardiff. Here we are:

<img src="images/2025-03-04ukrn_ils.jpeg" height = 400>

2025-01-14: republished on the LSE Impact Blog [Do Community Notes work?](https://blogs.lse.ac.uk/impactofsocialsciences/2025/01/14/do-community-notes-work/)

@@

2024-06-21: Research Matters magazine (with Shaun Leamon): [Experiments in research funding to reduce research bureaucracy](https://the-sra.org.uk/common/Uploaded%20files/Research%20Matters%20Magazine/sra-research-matters-june-2024-edition.pdf)
